Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-31 doc/manuscript/manuscript.Rmd
attempt to address methods in manuscript

## Isolate collection and DNA extraction {-}

@@

The white mold nurseries were 5m x 10m in size and maintained without applying fungicides to observe natural incidence of white mold.
The nursery plots were incorporated with a basal dressing of N:P:K = 1:3:2 and side dressing of 0:3:2 during the growing season.
Although the nursery locations were the same over sampling years, sampling plots within a location varied for sampling years.
Sampling of diseased tissue was carried out on a 'W' or 'V' shape transect, or randomly.
Because sampling depended on disease incidence, the number of samples isolated varied from year to year.
In total, we collected 366 isolates that were used in the present study.

@@

Table: (\#tab:isolate-table) Description of *Sclerotinia sclerotiorum* isolates used in this study.
N = Number of Isolates. 
Key abbreviations: wmn = white mold nursery, unk = unknown.

Each isolate was regenerated by activating one or several sclerotia according to the method described previously [@matheron1989in-vitro].
Once actively growing, mycelial compatibility group (MCG) and aggressiveness was determined for each isolate.
MCG was determined as described in @otto-hanson2011variation through co-culturing isolates in pairs on potato-dextrose agar (PDA) plates, where incompatibility of different MCGs resulted in formation of a mycelial barrier of dead tissue (barrage line) [@kohn1990mycelial].
Since MCGs are considered mutually exclusive, pairing was not required between all isolates in the study.

> SEE: Is that correct?  Perhaps consult with Becky or Rachana and then elaborate upon the sentence above.

Aggressiveness of each isolate was assessed using a straw test that rated necrotic lesion size on a scale from 1--9 with increasing aggressiveness [@petzoldt1996straw; @teran2006modified].

> SEE: Rating is not clear from the single sentence above.  On what plant host was it evaluated?  In the greenhouse?  What is a rating of 1 compared to a rating of 9 on the straw test?

@@

Of particular interest in this study was testing the association between mycelial compatibility groups (MCGs) and multilocus genotypes (MLGs).
In the past MCGs have been used as a proxy for clonal lineages [@leslie1993fungal; @otto-hanson2011variation; @kohn1995clonal; @carbone1999patterns; @lehner2015analysis]. 
When using genetic markers with MCGs, there are three basic relationship patterns, 1) One MLG to one MCG, 2) Several MLGs belong to one MCG, and 3) Several MCGs belong to one MLG, noting that 2 and 3 are not mutually exclusive.
Similar to what has been observed in other studies, our results show all three patterns (Fig. \@ref(biggraph)) [@aldrich-wolfe2015genetic; @carbone1999patterns; @attanayake2012genetic]. 
In contrast to other studies, we took a network approach to assessing the relationship between MCG and MLG and found no clear causality between MLGs and MCGs.

>>>>

## Isolate collection {-}

Several of the isolates used for this study were collected and reported in previous studies and were collected using the same methods [@otto-hanson2011variation].
Broadly, isolates were collected from two sources, white mold screening nurseries (wmn), or producer fields.
The white mold screening nurseries were 5m x 10m in size and maintained without applying fungicides to observe natural incidence of white mold.
The nursery plots were incorporated with a basal dressing of N:P:K = 1:3:2 and side dressing of 0:3:2 during the growing season [@steadman2003identification; @steadman2004identification; @steadman2005identification; @steadman2006identification; @otto2007identification].
Sampling was carried out by collecting diseased tissue in zig-zag transects across field plots. 
Because sampling depended on disease incidence, the number of samples isolated varied from year to year.
Although the nursery locations were the same over sampling years, sampling plots within a location varied for sampling years.

@@

Each isolate was regenerated by activating one or several sclerotia and transferring the leading edge of the mycelial mat according to the method described previously [@otto-hanson2011variation].
In combination with the 156 isolates described previously, we collected 210 isolates for a total of 366 isolates [@otto-hanson2011variation].

@@

Table: (\#tab:isolate-table) Description of *Sclerotinia sclerotiorum* isolates used in this study.
N = Number of Isolates. 
Key abbreviations: wmn = white mold screening nursery, unk = unknown.

## Mycelial Compatibility {-}

MCG was determined as described previously through co-culturing pairs of 2-day-old isolates 2.5cm apart on Diana Sermons (DS) Medium [@cubeta2001mycelial]. 
Incompatibility of different MCGs resulted in formation of a mycelial barrier of dead tissue (referred to as a barrage line) accompanied by the formation of sclerotia on either side of the barrage line, indicating the limits of the isolates' growth [@otto-hanson2011variation; @kohn1990mycelial; @leslie1993fungal].
Isolates were compared in a pairwise manner for each site and then representatives among sites were compared to determine mycelial compatibility groups by scoring compatible and incompatible interactions [@otto-hanson2011variation].

<!-- ![
Examples of mycelial compatibility results in *S. sclerotiorum*. 
A) Compatible reaction showing aerial hyphae.
B) Incompatible reaction showing barrage reaction of dead cells at point of contact.
](../../results/figures/publication/incompatibility2.JPG){#incompatibility width=25%} -->

## Aggressiveness {-}

Aggressiveness of each isolate was assessed using a straw test as carried out in @otto-hanson2011variation that rated necrotic lesion size [@petzoldt1996straw; @teran2006modified].
Briefly, the straw test uses 21-day-old G122 plants as the host in a greenhouse setting. 
Clear drinking straws cut to 2.5cm and sealed were used to place two mycelial plugs of inoculum on the host plant after removing the everything &gt;2.5cm above the fourth node.
Measurements were taken after 8 days using the Modified Petzoldt and Dickson scale where a score of 1--9 where 1 is no disease and 9 is plant death [@petzoldt1996straw; @teran2006modified].

@@

Of particular interest in this study was testing the association between mycelial compatibility groups (MCGs) and multilocus genotypes (MLGs).
In the past MCGs have been used as a proxy for clonal lineages [@leslie1993fungal; @otto-hanson2011variation; @kohn1990mycelial; @schafer2006optimized; @kohn1995clonal; @carbone1999patterns; @lehner2015genetic]. 
When using genetic markers with MCGs, there are three basic relationship patterns, 1) One MLG to one MCG, 2) Several MLGs belong to one MCG, and 3) Several MCGs belong to one MLG, noting that 2 and 3 are not mutually exclusive.
Similar to what has been observed in other studies, our results show all three patterns (Fig. \@ref(biggraph)) [@ford1995heterokaryon; @aldrich-wolfe2015genetic; @carbone1999patterns; @attanayake2012genetic].

@jo2008reassessment; @papaioannou2014barrage; @micali2003independence;
